Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-08-06 text/paper/paper1.tex
discussion section sec com

It is not a major obstacle for traditionalism to predict that global
readings are available. The weak variety of traditionalism holds that
the extra assumptions needed to derive global readings are not
standardly available, and so traditionalism is compatible with a lack
of observed global readings. Alternatively, traditionalists could
argue that the task's rather high processing demands lead to a
suppression of global implicature readings, in line with the findings
of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. Unfortunately, to the extent that global
readings are explained away, traditionalism also looses the
possibility of accounting for local readings of \as-sentences in its
unrestricted variety.\fn{Remember that what we called unrestricted
  traditionalism can account for local readings of \as-sentences by
  assuming that a sentence of the form \emph{Some of the $X$ are
    related to some of the $Y$} is a feasible alternative.} This is
because unrestricted traditionalism explains local and global readings
of \as-sentences in essentially the same manner. On top of that,
traditionalism cannot explain local readings for \es-sentences at
all. In sum, traditionalism alone cannot explain
(\ref{bsp:observed-preferences}), but needs an additional explanation
of local readings for \emph{both} \as- \emph{and} \es-sentences.

Grammaticalism, on the other hand, fails to predict the preference
relation in (\ref{bsp:observed-preferences}), because these strictly
contradict the strongest meaning hypothesis in either of its suggested
varieties.

>>>>

It is not a major obstacle for traditionalism to predict that global
readings are available. The weak variety of traditionalism holds that
the extra assumptions needed to derive global readings are not
standardly available, and so traditionalism is compatible with a lack
of observed global readings. Alternatively, traditionalists could
argue that the task's rather high processing demands lead to a
suppression of global implicature readings, in line with the findings
of \citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. Unfortunately, to the extent that global
readings are explained away as dispreferred or unavailable,
traditionalism also looses the possibility of accounting for local
readings of \as-sentences in its unrestricted variety.\fn{Remember
  that what we called unrestricted traditionalism can account for
  local readings of \as-sentences by assuming that a sentence of the
  form \emph{Some of the $X$ are related to some of the $Y$} is a
  feasible alternative.} This is because unrestricted traditionalism
explains local and global readings of \as-sentences in essentially the
same manner. On top of that, traditionalism cannot explain local
readings for \es-sentences at all. In sum, traditionalism alone cannot
explain (\ref{bsp:observed-preferences}), but needs an additional
explanation of local readings for \emph{both} \as- \emph{and}
\es-sentences.

Grammaticalism, on the other hand, fails to predict the preference
relation in (\ref{bsp:observed-preferences}), because these strictly
contradict the strongest meaning hypothesis in either of the two
varieties suggested by \citet{ChierchiaFox2008:The-Grammatical}. This
shows most clearly in the fact that both versions of the strongest
meaning hypothesis predict that local readings of \as-sentences are
preferred over literal ones. The problem, therefore, seems to be the
selection of readings by the strongest meaning hypothesis. In fact, if
(\ref{bsp:observed-preferences}) is the actual preference over
readings, then the strongest meaning hypothesis is also conceptually
on the wrong track, because no account that merely looks at the
logical strengths of readings can plausibly predict the preference
pattern in (\ref{bsp:observed-preferences}) for both \as- and
\es-sentences at the same time. (Try, if you please!) Turning away
from comparisons of logical strength, a selection criterion that
produces (\ref{bsp:observed-preferences}) is ready at hand: if we
assume that each insertion of $\exh(\cdot)$ operator is \emph{costly}
anti-proportional to the depth of its embedding, then we derive a
preference of literal readings over local ones over global ones. But
whether such an economy principle is sound and in line with further
empirical data is an interesting matter of further investigation. What
it does not explain in any case, is why some subjects in our study
gave local responses \emph{consistently}, while others did not. In
sum, in as far as grammaticalism depends on the strongest meaning
hypothesis, its predictive success is equally thin as that of
traditionalism.
